Hypertension and microbiome

### 2019-02-27 articletwo.Rmd
Minor

maaslin$lacto.max  <- maaslinwrapper(pseq = pseq.species.lactobacillus.core,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced =c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                          "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = paste0(lactotaxa collapse = ","))
```

@@

```{r save session}
save.image(file = paste0("cache/session-", now, ".Rdata"))
```

>>>>

maaslin$lacto.max  <- maaslinwrapper(pseq = pseq.species.lactobacillus.core,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced =c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                          "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = paste0(lactotaxa, collapse = ","))
```

@@

```{r save session}
save.image(file = paste0("rds/session-", now, ".Rdata"))
```
